### 2024-11-01 manuscript.tex
Add PIPERS reference

\begin{table}[t!]
\caption{Voyage, campaign and station publication references.}
\label{tab:voyage-references}
\small
\begin{tabular}{lp{14.5cm}}
\textbf{Name} & \textbf{References}\\
\hline
AA15-16  & \cite{klekociuk2020} \\
MARCUS   & \cite{mcfarquhar2016,mcfarquhar2019,zhang2017,keeler2017,walton2017,cromwell2017,mcfarquhar2021} \\
MICRE    & \cite{marchand2015,marchand2020,zhang2016,mcfarquhar2021} \\
PS77/2   & \cite{kniglanglo2011a,kniglanglo2011b,kniglanglo2011c,kniglanglo2014a,fahrbach2011} \\
PS77/3   & \cite{kniglanglo2011d,kniglanglo2011e,kniglanglo2012a,kniglanglo2014b,knust2011} \\
PS79/2   & \cite{kniglanglo2012b,kniglanglo2012c,kniglanglo2012d,kniglanglo2014c,kattner2012} \\
PS79/3   & \cite{kniglanglo2012e,kniglanglo2012f,kniglanglo2012g,kniglanglo2014d,wolfgladrow2012} \\
PS79/4   & \cite{kniglanglo2012h,kniglanglo2012i,kniglanglo2012j,kniglanglo2014e,lucassen2012} \\
PS81/2   & \cite{kniglanglo2013a,kniglanglo2013b,kniglanglo2013c,kniglanglo2014f,boebel2013} \\
PS81/3   & \cite{kniglanglo2013d,kniglanglo2013e,kniglanglo2013f,kniglanglo2014g,gutt2013} \\
PS81/4   & \cite{kniglanglo2013g,kniglanglo2013h,kniglanglo2013i,kniglanglo2014f,bohrmann2013} \\
PS81/5   & \cite{kniglanglo2013j,kniglanglo2013k,kniglanglo2013l,kniglanglo2014g,jokat2013} \\
PS81/6   & \cite{kniglanglo2013m,kniglanglo2013n,kniglanglo2013o,kniglanglo2014h,lemke2013} \\
PS81/7   & \cite{kniglanglo2013p,kniglanglo2013q,kniglanglo2014i,kniglanglo2016a,meyer2013} \\
PS81/8   & \cite{kniglanglo2013r,kniglanglo2014j,kniglanglo2014k,kniglanglo2014l,schlindwein2014} \\
PS81/9   & \cite{kniglanglo2014m,kniglanglo2014n,kniglanglo2014o,kniglanglo2014p,knust2014} \\
PS89     & \cite{kniglanglo2015a,kniglanglo2015b,kniglanglo2015c,kniglanglo2015d,boebel2016}\\
PS96     & \cite{kniglanglo2016b,kniglanglo2016c,kniglanglo2016d,kniglanglo2016e,schrder2017} \\
PS97     & \cite{kniglanglo2016f,kniglanglo2016g,kniglanglo2016h,kniglanglo2016i,lamy2017} \\
PS103    & \cite{kniglanglo2017a,kniglanglo2017b,kniglanglo2017c,kniglanglo2017d,boebel2018} \\
PS104    & \cite{kniglanglo2017e,kniglanglo2017f,kniglanglo2017g,gohl2018,schmithsen2021a} \\
PS111    & \cite{schmithsen2019a,schmithsen2020a,schmithsen2021b,schmithsen2021c,schrder2018} \\
PS112    & \cite{schmithsen2019b,schmithsen2020b,schmithsen2021d,schmithsen2021e,meyer2018} \\
PS117    & \cite{schmithsen2019c,schmithsen2020c,schmithsen2021f,schmithsen2021g,boebel2019} \\
PS118    & \cite{schmithsen2019d,schmithsen2020d,schmithsen2021h,schmithsen2021i,dorschel2019} \\
PS123    & \cite{schmithsen2021j,schmithsen2021m,schmithsen2021n,schmithsen2021k,hoppmann2023} \\
PS124    & \cite{schmithsen2021o,schmithsen2021q,schmithsen2021p,hoppmann2023} \\
TAN1802  & \cite{kremser2020,kremser2021} \\
\end{tabular}
\end{table}

>>>>

\begin{table}[t!]
\caption{Voyage, campaign and station publication references.}
\label{tab:voyage-references}
\small
\begin{tabular}{lp{14.5cm}}
\textbf{Name} & \textbf{References}\\
\hline
AA15-16  & \cite{klekociuk2020} \\
MARCUS   & \cite{mcfarquhar2016,mcfarquhar2019,zhang2017,keeler2017,walton2017,cromwell2017,mcfarquhar2021} \\
MICRE    & \cite{marchand2015,marchand2020,zhang2016,mcfarquhar2021} \\
NBP1704  & \cite{ackley2020} \\
PS77/2   & \cite{kniglanglo2011a,kniglanglo2011b,kniglanglo2011c,kniglanglo2014a,fahrbach2011} \\
PS77/3   & \cite{kniglanglo2011d,kniglanglo2011e,kniglanglo2012a,kniglanglo2014b,knust2011} \\
PS79/2   & \cite{kniglanglo2012b,kniglanglo2012c,kniglanglo2012d,kniglanglo2014c,kattner2012} \\
PS79/3   & \cite{kniglanglo2012e,kniglanglo2012f,kniglanglo2012g,kniglanglo2014d,wolfgladrow2012} \\
PS79/4   & \cite{kniglanglo2012h,kniglanglo2012i,kniglanglo2012j,kniglanglo2014e,lucassen2012} \\
PS81/2   & \cite{kniglanglo2013a,kniglanglo2013b,kniglanglo2013c,kniglanglo2014f,boebel2013} \\
PS81/3   & \cite{kniglanglo2013d,kniglanglo2013e,kniglanglo2013f,kniglanglo2014g,gutt2013} \\
PS81/4   & \cite{kniglanglo2013g,kniglanglo2013h,kniglanglo2013i,kniglanglo2014f,bohrmann2013} \\
PS81/5   & \cite{kniglanglo2013j,kniglanglo2013k,kniglanglo2013l,kniglanglo2014g,jokat2013} \\
PS81/6   & \cite{kniglanglo2013m,kniglanglo2013n,kniglanglo2013o,kniglanglo2014h,lemke2013} \\
PS81/7   & \cite{kniglanglo2013p,kniglanglo2013q,kniglanglo2014i,kniglanglo2016a,meyer2013} \\
PS81/8   & \cite{kniglanglo2013r,kniglanglo2014j,kniglanglo2014k,kniglanglo2014l,schlindwein2014} \\
PS81/9   & \cite{kniglanglo2014m,kniglanglo2014n,kniglanglo2014o,kniglanglo2014p,knust2014} \\
PS89     & \cite{kniglanglo2015a,kniglanglo2015b,kniglanglo2015c,kniglanglo2015d,boebel2016}\\
PS96     & \cite{kniglanglo2016b,kniglanglo2016c,kniglanglo2016d,kniglanglo2016e,schrder2017} \\
PS97     & \cite{kniglanglo2016f,kniglanglo2016g,kniglanglo2016h,kniglanglo2016i,lamy2017} \\
PS103    & \cite{kniglanglo2017a,kniglanglo2017b,kniglanglo2017c,kniglanglo2017d,boebel2018} \\
PS104    & \cite{kniglanglo2017e,kniglanglo2017f,kniglanglo2017g,gohl2018,schmithsen2021a} \\
PS111    & \cite{schmithsen2019a,schmithsen2020a,schmithsen2021b,schmithsen2021c,schrder2018} \\
PS112    & \cite{schmithsen2019b,schmithsen2020b,schmithsen2021d,schmithsen2021e,meyer2018} \\
PS117    & \cite{schmithsen2019c,schmithsen2020c,schmithsen2021f,schmithsen2021g,boebel2019} \\
PS118    & \cite{schmithsen2019d,schmithsen2020d,schmithsen2021h,schmithsen2021i,dorschel2019} \\
PS123    & \cite{schmithsen2021j,schmithsen2021m,schmithsen2021n,schmithsen2021k,hoppmann2023} \\
PS124    & \cite{schmithsen2021o,schmithsen2021q,schmithsen2021p,hoppmann2023} \\
TAN1802  & \cite{kremser2020,kremser2021} \\
\end{tabular}
\end{table}
